---
title: 'Outside The Yellow: A Review of Leasing Activity Over the Last 12 Months'
author: David
date: '2018-04-12'
slug: outside-the-yellow-a-review-of-leasing-activity-over-the-last-12-months
categories:
  - leasing activity
  - Peer Analysis
tags:
  - leasing activity
  - Competior Analysis
---


####**Data Sources and Methodology**

* Downloaded all lease activity for the prior twelve months using DrillingInfo.
* Joined leases level data to sections for mapping purposes.
* Identied trends in company leasing activity.
* Based on the previous twelve month time period in the Permian Basin, there are **~150,000** more records in the database compared to the DI landtrac system and is about a month ahead on filings.

####**Highlights**

* **Continental Resources** expanding its New Mexico *stealth* play into the Northern Midland Basin.
    + Beginning in the 2H of 2017, the company began acquiring leases in **Andrews, Dawson and Gaines** Counties.
    + Continental recently permitted wells in New Mexico.
* **Devon Energy** has filed multiple leases in **Brewster County** near Apache's Alpine High play during 3Q'17.
    + In 2017, the company had a rig running in the area, but has seen relatively no activity since then.
* After selling out to Parsley, **Double Eagle** is back at it with leases filed in the Southern Delaware, Central Basin Platform and Midland Basin.
    + A scatter shot of leases have been filed in the **San Andreas** play around Seminole and also in the Eastern Midland Basin in **Scurry County.**
* Use the map to filter by company and time period. The reset filter will add all polygons back on the map.    
<br>
<br>

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center',echo=F,warning=F,message=F,asis=F)
```



```{r}
Sys.setenv('MAPBOX_TOKEN' = 'pk.eyJ1IjoiZG1hdXBpbmNlaCIsImEiOiJjamZtbWhqdHMwdTQzMzNvZGdpc2x4bzlxIn0.eIDdIjeaDK-x7Q8uZgdJGg')
```



```{r}
library(sf)
library(tidyverse)
library(plotly)
library(rgdal)
library(crosstalk)
```

```{r}
leases<- readOGR(".",'lease_master_dissolve',verbose=F)
cxo_leases<- readOGR(".",'cxo_leases_2.21.18',verbose=F)

leases<-st_as_sf(leases)
cxo_leases<- st_as_sf(cxo_leases)
```

```{r}
colors<-c('#FF355E','red','blue','purple','#FF6037','#FF9933','#FFFF66','#CCFF00','#AAF0D1','#FF6EFF','#FF00CC')

#colors<- makeTransparent(colors, alpha=.65)
colors= rep_len(colors,length.out=769)
Alias= unique(leases$Alias)

color_frame<- data.frame(colors,Alias)


leases<- left_join(leases,color_frame)

leases$Reset_Filter='RESET'

colnames(leases)[4]<-'Acres'

```


```{r}
leases_sd<- SharedData$new(leases)


bscols(widths=c(3,NA),list(filter_select('Alias','Lesee',leases_sd,~Alias),
        filter_select('YearQtr','YearQtr',leases_sd,~YearQtr),                   
       filter_select("Reset Filter","Reset Filter",leases_sd,~ifelse(Reset_Filter=="RESET","YES","NO"))),
  plot_mapbox(alpha=.65) %>%
    add_sf(data=cxo_leases,fillcolor='grey',stroke=NA)%>%
    add_sf(data=leases_sd,fillcolor=~colors,stroke=NA,hoverinfo = 'text',
        text = ~paste('</br> Lesee: ', Alias,
                      '</br> Gross Acres: ', Acres,
                      '</br> Date: ', YearQtr))%>%
    layout(showlegend=FALSE,
    mapbox = list(zoom=8,style = "light")))

```

