---
title: 'Outside The Yellow: A Review of Leasing Activity Over the Last 12 Months'
author: David
date: '2018-04-12'
slug: outside-the-yellow-a-review-of-leasing-activity-over-the-last-12-months
categories:
  - leasing activity
  - Peer Analysis
tags:
  - leasing activity
  - Competior Analysis
---


####**Data Sources and Methodology**

* Compiled all lease level activity for the prior twelve months using DrillingInfo.
* Analyzed leases documents, memos of leases, extensions and lease amendments in order to identify trends in company leasing activity.
 

####**Highlights**

* **Continental Resources** is expanding its position in the Northern Midland Basin which they began acquiring in late 2016.
    + Activity in the fourth quarter and first quarter of 2018 has been concentrated in **Southeast Gaines County,** where the bulk of their acreage is **offsetting Murphy's in Dawson County.**
    + The company has also recently permitted two horizontal wells on its Northern Delaware position in New Mexico.
* After selling out to Parsley, **Double Eagle** is back at it with leases filed in the Southern Delaware, Central Basin Platform and Midland Basin.
    + A scatter shot of leases have been filed in the **San Andres** play around Seminole and also in the Eastern Midland Basin in **Scurry County.**
        + The company's Scurry County acreage is offsetting private operator King Operating.
    + In the fourth quarter, Double Eagle began acquiring leases in **Northeast Martin County** under **DE Midland III.**
* Multiple operators filed leases around **North Harpoon** during the first quarter of 2018.
    + **Double Eagle** filed a lease within North Harpoon on 160 acres.
* **Devon Energy** had multiple lease filings in **Brewster County** near Apache's Alpine High play during the third quarter.
    + In 2017, the company drilled a single vertical wildcat on its acreage however, there has been no activity since then. 
* Use the map to filter by date, company and instrument type.    
<br>
<br>

####**Twelve Month Activity Map**
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center',echo=F,warning=F,message=F,asis=F)
```



```{r}
Sys.setenv('MAPBOX_TOKEN' = 'pk.eyJ1IjoiZG1hdXBpbmNlaCIsImEiOiJjamZtbWhqdHMwdTQzMzNvZGdpc2x4bzlxIn0.eIDdIjeaDK-x7Q8uZgdJGg')
```



```{r}
library(sf)
library(tidyverse)
library(plotly)
library(rgdal)
library(crosstalk)
library(leaflet)
library(htmltools)
```

```{r,echo=F,warning=F,message=F,verbose=F}
leases<- readOGR(".",'lease_master2',verbose=F)
cxo_leases<- readOGR(".",'cxo_leases_2.21.18',verbose=F)
#counties <- readOGR(".","counties",verbose = F)
```


```{r}
df<- openxlsx::read.xlsx("LeasingActivity_4-17_4-18.xlsx",sheet=1)
```


```{r}
Color<-rep_len(c('#00ccff','#ff9999','#cc0066','#00264d','#ff0000','#003300',"#e60000",'#99ffff',"#cc9966",'#ff9966','#0d0d0d',"#cc33ff",'#ff5500',"#ccffee","#ff9900","#0000e6",'#660066','#33ffd6','#0099ff','#a6a6a6','#0000ff','#ff00ff','#ff0066','#ffd699','#ffffb3'," dark blue",'#66ff99','#a64dff',"maroon",'#000066',"#e65c00",'#339966',"#0099cc",
"#800000","#00ffcc","#660066","#ffa31a","red","blue","purple","light green","dark blue","#ccffcc","#3333cc","#b35900","black","#bf4040","#666699","#ad33ff","#ffb3cc","green","purple","#ffb833"),length.out=766)


leases<-st_as_sf(leases)

leases<- leases%>% mutate(Alias= replace(Alias, which(grepl("ROSETTA",Alias)),"NOBLE"),Alias)
leases<- leases%>% mutate(Alias= replace(Alias, which(grepl("DE MGMT|DE MIDLAND III",Alias)),"DOUBLE EAGLE"),Alias)

Alias<- unique(leases$Alias)
color_frame<- data.frame(Color,Alias)

leases<-left_join(leases,color_frame, by="Alias")

leases$Ar__Ac_<- round(as.numeric(leases$Ar__Ac_),0)
leases$Ar__Ac_<- as.character(leases$Ar__Ac_)
leases$Rcrd_Dt<- zoo::as.Date(as.character(leases$Rcrd_Dt))



leases<- as(leases,"Spatial")


#pal <- colorFactor(palette = unique(as.character(tx_nm_permits$Color)),domain=tx_nm_permits$Top20,levels=tx_nm_permi#ts$Top20,ordered=T)


leases$Reset_Filter='RESET'


leases@data$YearQtr<- as.character(leases@data$YearQtr)
```

```{r}
labs <- lapply(seq(nrow(leases@data)), function(i) {
  paste0("Lessee: ", leases@data[i, "Alias"], '<p>',
         "Instrument Type: ", leases@data[i, "Instr_T"],'<p>',
         "Acquisition Quarter: ", leases@data[i, "YearQtr"],'<p>',
         "Gross Acres: ",leases@data[i, "Ar__Ac_"],'<p>',
         "Transaction Date: ", leases@data[i,'Rcrd_Dt']) 
})

```


```{r}
leases_sd<- SharedData$new(leases)
 
#Added this to allow sharedDate to work ()

leases_sd_df <- SharedData$new(leases@data, group = leases_sd$groupName())
```


```{r}
bscols(widths=c(3,NA),list(filter_slider("Rcrd_Dt","Record Date",leases_sd_df,~Rcrd_Dt),
        filter_select('Alias','Lessee',leases_sd_df,~Alias),
        filter_select('YearQtr','Date By Quarter',leases_sd_df,~YearQtr),
        filter_select('Instr_T','Instrument Type',leases_sd_df,~Instr_T)
        ),
      leaflet(leases_sd,width="100%",height = 550) %>%
  # Base groups
  addTiles(group = "Esri.WorldTopoMap")%>%
  addProviderTiles(providers$Esri.WorldTopoMap)%>%
  addPolygons(data=cxo_leases,fillColor='yellow',fillOpacity = .4,stroke=NA)%>%
  addPolygons(data=leases_sd,fillColor = ~Color,fillOpacity = .75,stroke=NA,label=lapply(labs,HTML))%>% setView(lng=-102.79, lat=31.89,zoom=7)
)


```
<br>
<br>
