---
title: Recent Transactions and Current Deals On The Market
author: David Maupin
date: '2018-04-10'
slug: recent-transactions-and-current-deals-on-the-market
categories:
  - Mergers and Acquisitions
  - Current Deals
tags:
  - Mergers and Acquisitions
  - Current Deals
description: "Mapping recent transactions and current deals on the market. Data sourced from PLS starting in 2017."
---


####**Data Sources and Methodology**

* Data obtained from PLS and filtered to show relevant transactions and current deals on the market.
* Select active deals or previous M&A activity in the map.
* Table includes current deals.

####**Select Highlights**

* **Three Rivers Operating III** (Riverstone backed) recently divested it's ~60,000 acre position in Culberson County.
    + Riverstone stated they received a ROI of ~2.2 from its initial investment of ~$94 million which represents total proceeds of ~$205 million.
    + The total price paid is currently unknown.
* Rumored buyer is **Admiral Permian** (ex Reliance) which received an equity line of **$600 million** from Pinebrook in March of 2017.
* Announcement was somewhat surprising as well results in the area have been underwhelming.
* Bloomberg reported that Shell is potentially interested in acquiring BHP's Delaware Basin assets.
    + *"BHP has good assets that overlap our own acreage in the Permian, and may be interesting for us."*
    

<br>
<br>


```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center',echo=F,warning=F,message=F,asis=F)
```


```{r}
library(geojsonio)
library(leaflet.extras)
library(spatialEco)
library( htmltools )
library(tidyverse)
library(sf)
library(crosstalk)
library(plotly)
library(listviewer)
```


```{r}
Sys.setenv('MAPBOX_TOKEN' = 'pk.eyJ1IjoiZG1hdXBpbmNlaCIsImEiOiJjamZtbWhqdHMwdTQzMzNvZGdpc2x4bzlxIn0.eIDdIjeaDK-x7Q8uZgdJGg')
```


```{r}
sold <- geojson_read("Sold_Deals.json",
  what = "sp")

net_acres<- openxlsx::read.xlsx("Net_Acres.xlsx",sheet=1)
net_acres<- net_acres%>%select(id,Net.Acres)


sold$date_announced<- as.Date(sold$date_announced)
sold$Year<- format(sold$date_announced,'%Y')
```



```{r}
sold<- sp.na.omit(sold, col.name = 'X__Acre')


sold@data$X__Acre<- as.numeric(as.character(sold@data$X__Acre))
sold@data$value___MM_<- as.numeric(as.character(sold@data$value___MM_))

sold<- sold[sold$X__Acre > 1000,]

sold$Net_Acres<- sold$value___MM_*1000000/sold$X__Acre

#tbl<- sold@data
#tbl<- tbl%>% select(buyers, sellers, id,headline)%>%distinct()
#write.csv(tbl,"tbl2.csv")
net_acres$id<- as.character(net_acres$id)
sold@data$id<- as.character(sold@data$id)

sold@data<- left_join(sold@data,net_acres)

sold$Net.Acres<- paste(prettyNum(sold$Net.Acres,big.mark = ","),sep="")
sold$PricePerAcre<- paste("$",prettyNum(sold$X__Acre,big.mark = ","),sep="")


```



```{r}
sold<- st_as_sf(sold)
sold<- sold%>% select(buyers,sellers,Net_Acres, geometry,Year,value___MM_,X__Acre,hexColor)
```

```{r}
deals_on_mkt <- geojson_read("Deals_On_Market.json",
  what = "sp")

deals_on_mkt<- st_as_sf(deals_on_mkt)




```



```{r,eval=F}
pal <- colorFactor(c("yellow","blue","green","orange","purple","black","#ace600","#00ffff","#666633"), sold$id)

deal_pal <- colorFactor(c("#ffe6ea","#ff99aa","#ff1a40","#e60073"),deals_in_play$id)


labs <- lapply(seq(nrow(sold@data)), function(i) {
  paste0("Buyer: ", sold@data[i, "buyers"], '<p>',
         "Net Acres: ", sold@data[i, "Net.Acres"],'<p>',
         "$/Acre: ",sold@data[i, "PricePerAcre"],'<p>',
         "Seller: ",sold@data[i, "sellers"],'<p>',
         "Transaction Date: ", sold@data[i,'date_announced']) 
})

leaflet() %>%addTiles(group = "Esri.WorldTopoMap")%>%
  addProviderTiles(providers$Esri.WorldTopoMap)%>%
  addPolygons(data=sold, weight = 1, color = "#000000",
              fillColor=~pal(id),
              fillOpacity=0.7,label=lapply(labs,HTML),
              highlightOptions = highlightOptions(
                color='red', opacity = 1, weight = 1.5, fillOpacity = 1,
                bringToFront = TRUE, sendToBack = TRUE),
              group="Transacted Deals") 
  addLayersControl(
    baseGroups=c("Transacted Deals","Deals In Play"),
    position = "topleft",
    options = layersControlOptions(collapsed = FALSE)
  )%>%
  addFullscreenControl( pseudoFullscreen = T)%>%suspendScroll()%>% addScaleBar(position="topleft")

#update

```
<br>
<br>

```{r}
sold<- st_as_sf(sold)
sold$Reset_Filter<- 'RESET'
sold$colors= rep_len(c('#FF355E','red','blue','purple','#FF6037','#FF9933','#FFFF66','#CCFF00','#AAF0D1','#FF6EFF','#FF00CC'),length.out=200)
```

```{r}
sd_sold<- SharedData$new(sold)


bscols(widths=c(3,NA),list(filter_select('buyers','Acquirer',sd_sold,~buyers),
       filter_select("Reset Filter","Reset Filter",sd_sold,~ifelse(Reset_Filter=="RESET","YES","NO"))),
  plot_mapbox() %>%
    add_sf(data=sd_sold,fillcolor=~colors,stroke=NA,hoverinfo = 'text',
        text = ~paste('</br> Acquirer: ', buyers,
                '</br> Seller: ', sellers,
                '</br> Price Per Acre: ', X__Acre,
                '</br> Total Price (MM): ', value___MM_,
                '</br> Year of Acquisition ', Year))%>%
    layout(showlegend=FALSE,
    mapbox = list(zoom=7,style = "light")))


```



