---
title: Recent Transactions and Current Deals On The Market
author: David Maupin
date: '2018-02-21'
slug: recent-transactions-and-current-deals-on-the-market
categories:
  - Mergers and Acquisitions
  - Current Deals
tags:
  - Mergers and Acquisitions
  - Current Deals
description: "Mapping recent transactions and current deals on the market. Data sourced from PLS starting in 2017."
---


####**Data Sources and Methodology**

* Data obtained from PLS and filtered to show relevant transactions and current deals on the market.
* Select active deals or previous M&A activity in the map.
* Table includes current deals.

####**Select Highlights**

* **Three Rivers Operating III** (Riverstone backed) recently divested it's ~60,000 acre position in Culberson County.
    + Riverstone stated they received a ROI of ~2.2 from its initial investment of ~$94 million which represents total proceeds of ~$205 million.
    + The total price paid is currently unknown.
* Rumored buyer is **Admiral Permian** (ex Reliance) which received an equity line of **$600 million** from Pinebrook in March of 2017.
* Announcement was somewhat surprising as well results in the area have been underwhelming.
* Bloomberg reported that Shell is potentially interested in acquiring BHP's Delaware Basin assets.
    + *"BHP has good assets that overlap our own acreage in the Permian, and may be interesting for us."*
    

<br>
<br>


```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center',echo=F,warning=F,message=F,asis=F)
```


```{r}
library(geojsonio)
library(leaflet.extras)
library(spatialEco)
library( htmltools )
library(rgdal)
library(tidyverse)
```


```{r}
shp <- geojson_read("Geojson.json",
  what = "sp")

lilis <- readOGR(".","Lil_One_01_31_18_MA_Shapefile_63589",verbose =F)

lilis@data$NetAcre<-"2,798"

deals_in_play<- readOGR(".","listingGeometryViewDEVPolygon",verbose = F)


bhp<- readOGR(".","BHP",verbose = F)
cxo_leases<- readOGR(".","cxo_leases_2.21.18",verbose = F)

net_acres<- openxlsx::read.xlsx("Net_Acres.xlsx",sheet=1)
net_acres<- net_acres%>%select(id,Net.Acres)
```




```{r}
shp<- sp.na.omit(shp, col.name = 'X__Acre')


shp<- shp[!grepl("Franco-Nevada Corp|Viper Energy Partners LP|WildHorse Resource Development Corp",shp$buyers),]
shp<- shp[grepl("Unconventional",shp$US_play),]


shp@data$X__Acre<- as.numeric(as.character(shp@data$X__Acre))
shp@data$value___MM_<- as.numeric(as.character(shp@data$value___MM_))

shp<- shp[shp$X__Acre > 1000,]

shp$Net_Acres<- shp$value___MM_*1000000/shp$X__Acre

#tbl<- shp@data
#tbl<- tbl%>% select(buyers, sellers, id,headline)%>%distinct()
#write.csv(tbl,"tbl2.csv")
net_acres$id<- as.character(net_acres$id)
shp@data$id<- as.character(shp@data$id)

shp@data<- left_join(shp@data,net_acres)

shp$Net.Acres<- paste(prettyNum(shp$Net.Acres,big.mark = ","),sep="")
shp$PricePerAcre<- paste("$",prettyNum(shp$X__Acre,big.mark = ","),sep="")

lilis$DOLACRE<- paste("$",prettyNum(lilis$DOLACRE,big.mark = ","),sep="")
```



```{r}
deals_in_play<- deals_in_play[!grepl("Minerals|Royalty|Prospects",deals_in_play$DealType),]

three_riv= deals_in_play[grepl("Three Rivers",deals_in_play$Seller),]
deals_in_play= deals_in_play[!grepl("Three Rivers",deals_in_play$Seller),]




labs_deals <- lapply(seq(nrow(deals_in_play@data)), function(i) {
  paste0("Seller: ", deals_in_play@data[i, "Seller"], '<p>',
         "Producing Wells/Net Acreage: ", deals_in_play@data[i,"WellsAcrea"], 
         "Deal Type: ",deals_in_play@data[i,'DealType'],'<p>',
         "Listing Date: ", deals_in_play@data[i,'listing_Da']) 
})


bhp$Net_Acres<- paste(prettyNum(bhp$Net_Acres,big.mark = ","),sep="")
bhp$Production<- paste(prettyNum(bhp$Production,big.mark = ","),sep="")



labs_bhp<- lapply(seq(nrow(bhp@data)), function(i) {
  paste0("Seller: ",bhp@data[i, "Company"], '<p>',
         "Producing Wells/Net Acreage: ", bhp@data[i,"Net_Acres"],'<p>',
         "Current Production: ",bhp@data[i,'Production']) 
})


labs_lilis <- lapply(seq(nrow(lilis@data)), function(i) {
  paste0("Buyer: ", lilis@data[i, "BUYERS"], '<p>',
         "Net Acres: ", lilis@data[i, "NetAcre"],'<p>',
         "$/Acre: ",lilis@data[i, "DOLACRE"],'<p>',
         "Seller: ",lilis@data[i, "SELLERS"],'<p>',
         "Transaction Date: ", lilis@data[i,'ANNDATE']) 
})


```


```{r}
  


three_riv$Buyer= "Admiral Permian"

labs_three_riv <- lapply(seq(nrow(three_riv@data)), function(i) {
  paste0("Seller: ", three_riv@data[i, "Seller"], '<p>',
         "Buyer: ", three_riv@data[i, "Buyer"], '<p>',
         "Producing Wells/Net Acreage: ", three_riv@data[i,"WellsAcrea"], 
         "Deal Type: ",three_riv@data[i,'DealType'],'<p>',
         "Listing Date: ", three_riv@data[i,'listing_Da']) 
})





x= shp@data

```



```{r}
pal <- colorFactor(c("yellow","blue","green","orange","purple","black","#ace600","#00ffff","#666633"), shp$id)

deal_pal <- colorFactor(c("#ffe6ea","#ff99aa","#ff1a40","#e60073"),deals_in_play$id)


labs <- lapply(seq(nrow(shp@data)), function(i) {
  paste0("Buyer: ", shp@data[i, "buyers"], '<p>',
         "Net Acres: ", shp@data[i, "Net.Acres"],'<p>',
         "$/Acre: ",shp@data[i, "PricePerAcre"],'<p>',
         "Seller: ",shp@data[i, "sellers"],'<p>',
         "Transaction Date: ", shp@data[i,'date_announced']) 
})



leaflet() %>%addTiles(group = "Esri.WorldTopoMap")%>%
  addProviderTiles(providers$Esri.WorldTopoMap)%>%
  addPolygons(data=cxo_leases,stroke=F, fillColor = "grey",fillOpacity = .5,color=NA)%>%
  addPolygons(data=shp, weight = 1, color = "#000000",
              fillColor=~pal(id),
              fillOpacity=0.7,label=lapply(labs,HTML),
              highlightOptions = highlightOptions(
                color='red', opacity = 1, weight = 1.5, fillOpacity = 1,
                bringToFront = TRUE, sendToBack = TRUE),
              group="Transacted Deals") %>%
  addPolygons(data=lilis, weight = 1, color = "#000000",
              fillColor="#0033cc",
              fillOpacity=0.7,label=lapply(labs_lilis,HTML),
              highlightOptions = highlightOptions(
                color='red', opacity = 1, weight = 1.5, fillOpacity = 1,
                bringToFront = TRUE, sendToBack = TRUE),
              group="Transacted Deals")%>%
  addPolygons(data=three_riv, weight = 1, color = "#000000",
              fillColor="purple",
              fillOpacity=0.7,label=lapply(labs_three_riv,HTML),
              highlightOptions = highlightOptions(
                color='#00ff00', opacity = 1, weight = 1.5, fillOpacity = 1,
                bringToFront = TRUE, sendToBack = TRUE),
              group="Transacted Deals") %>%
  addPolygons(data=deals_in_play, weight = 1, color = "#000000",
              fillColor=~deal_pal(id),
              fillOpacity=0.7,label=lapply(labs_deals,HTML),
              highlightOptions = highlightOptions(
                color='#00ff00', opacity = 1, weight = 1.5, fillOpacity = 1,
                bringToFront = TRUE, sendToBack = TRUE),
              group="Deals In Play") %>%
  addLayersControl(
    baseGroups=c("Transacted Deals","Deals In Play"),
    position = "topleft",
    options = layersControlOptions(collapsed = FALSE)
  )%>%
  addPolygons(data=bhp, weight = 1, color = "#000000",
              fillColor="red",
              fillOpacity=0.7,label=lapply(labs_bhp,HTML),
              highlightOptions = highlightOptions(
                color='#00ff00', opacity = 1, weight = 1, fillOpacity = 1,
                bringToFront = TRUE, sendToBack = TRUE),
              group="Deals In Play") %>%
  addLayersControl(
    baseGroups=c("Transacted Deals","Deals In Play"),
    position = "topleft",
    options = layersControlOptions(collapsed = FALSE)
  )%>%
  addFullscreenControl( pseudoFullscreen = T)%>%suspendScroll()%>% addScaleBar(position="topleft")

```
<br>
<br>

#####**Deals In Play**
```{r,echo=F}
table<-DT::datatable(deals_in_play@data[,c(12,5,11,33,32,14)],class = 'cell-border stripe',filter='top',extensions='Buttons',
                     options = list(dom = 'Bfrtip',
                                    buttons= c('csv','pdf'),
    columnDefs = list(list(className = 'dt-center', targets = 5)),
     pageLength = 10, lengthMenu = c(10,20,30,40,50)),
  fillContainer = T)
widgetframe::frameWidget(table,width='100%')
```
<br>
***Using Google Chrome,** open csv by right clicking and selecting show in folder. Rename file with **EXAMPLE.csv** which can then be saved as an excel document.*
